The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
couple added todos

### Network metrics
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals, relevance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the edge, for each individual for
each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Degree centrality, the number of direct connections an individual
has to other individuals in the network, is the basis of many calculations
[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
we measured the connective redundancy, the proportion of neighbours repeated in
multiple layers, and the layer relevance, the proportion of neighbours present
in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].

@@

Although multilayer animal social networks are relatively novel (Silk et al.
2018), movement behaviour within multilayer networks has already been considered
in a couple studies. In vulturine gunieafowl (*Acryllium vulturinum*), GPS
movement data were used to generate *monolayer* association networks within a
multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks*
are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node (Mourier et al. 2019). While both studies integrate
movement in some capacity, neither generate networks based on continuous
measures of dyadic or collective movement (Long et al. 2014).

>>>>

### Network metrics
<!-- TODO: expand + simplify + examples individual A, B etc -->
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals, relevance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the edge, for each individual for
each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Degree centrality, the number of direct connections an individual
has to other individuals in the network, is the basis of many calculations
[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
we measured the connective redundancy, the proportion of neighbours repeated in
multiple layers, and the layer relevance, the proportion of neighbours present
in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].

@@

<!-- remove italics from terms? -->
Although multilayer animal social networks are relatively novel (Silk et al.
2018), movement behaviour within multilayer networks has already been considered
in a couple studies. In vulturine gunieafowl (*Acryllium vulturinum*), GPS
movement data were used to generate *monolayer* association networks within a
multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks*
are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node (Mourier et al. 2019). While both studies integrate
movement in some capacity, neither generate networks based on continuous
measures of dyadic or collective movement (Long et al. 2014).
